Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex\\ over domains with shellable triangulations

### 2024-07-04 main.tex
Update on Overleaf.

We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where $C_{\rm{EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
\begin{align}
    C_{\rm{EFNT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align}
Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{|1-\frac 2 p|}C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align}
In the limit case $p=1$, the optimal Poincar\'e constant $1/2$ also coincides with the optimal Poincar\'e--Friedrichs constant, as can verified with some one-dimensional example. % TODO Acosta-Duran %\footnote{In the case $p=1$, the optimal Poincar\'e constant $1/2$ is an upper bound for the optimal Poincar\'e--Friedrichs constant. When $\Omega = (0,1)$, then $u(x) = x - 0.5$ is }
Finally, since convex domains are Lipschitz domains: 
\begin{align}\label{math:lipschitzestimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{\infty}(\Omega)}
    \leq 
    \diam(\Omega)
    \| \nabla u \|_{L^{\infty}(\Omega)}
    ,
    \quad 
    u \in W^{1,\infty}(\Omega)
    .
\end{align}

>>>>

We know optimal Poincar\'e--Friedrichs constants over convex domains~(\cite[Theorem~1.1]{ferone2012remark}\cite[Theorem~1.1]{esposito2013poincare}): 
when $1 < p < \infty$, one can show that 
\begin{align}\label{math:esposito:pf}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align}
where $C_{\rm{EFNT},p}$ is the best possible constant that only depends on $p$ and equals 
\begin{align}
    C_{\rm{EFNT},p}
    :=
    \frac{ p \sin(\pi/p) }{ 2\pi \sqrt[p]{p-1} }
    .
\end{align}
Note that the last inequalities imply, again when $1 < p < \infty$, the Poincar\'e inequalities
\begin{align}\label{math:esposito:poincare}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    2^{|1-\frac 2 p|}C_{\rm{EFNT},p}
    \diam(\Omega)
    \| \nabla u \|_{L^{p}(\Omega)}
    ,
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align}
In the limit case $p=1$, the optimal Poincar\'e constant $1/2$ also bounds the Poincar\'e--Friedrichs constant:
\begin{align}\label{math:l1estimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{1}(\Omega)}
    \leq 
    \frac{ \diam(\Omega) }{2}
    \| \nabla u \|_{L^{1}(\Omega)}
    ,
    \quad 
    u \in W^{1,1}(\Omega)
    .
\end{align}
In the limit case $p=\infty$, since convex domains are Lipschitz domains, Rademacher's theorem leads to 
\begin{align}\label{math:lipschitzestimate}
    \min\limits_{ c \in \bbR }
    \| u - c \|_{L^{\infty}(\Omega)}
    \leq 
    \diam(\Omega)
    \| \nabla u \|_{L^{\infty}(\Omega)}
    ,
    \quad 
    u \in W^{1,\infty}(\Omega)
    .
\end{align}

\begin{example}
    Let $\Omega = (-1,1)$ and consider the family of odd function $u_{t} : \Omega \rightarrow \bbR$ for $t \in (0,1)$ 
    that satisfy $u_{t}(0)=0$, $u_{t}(t) = 1$ and $u_t(1) = 1$ and interpolate linearly between those points. 
    Obviously,
    \begin{align}
        \| u_{t} \|_{L^{1}(\Omega)} = 2 - t,
        \qquad 
        \| u'_{t} \|_{L^{1}(\Omega)} = 2t \frac{2}{2t} = 2.
        ,
    \end{align}
    and $\Omega$ has diameter $2$. As $u_t$ has average zero, this example shows that \eqref{math:acostaduran} is optimal. 
    At the same time, for any constant $c \in \bbR$ we have $\| u_t - c \|_{L^1(\Omega)} = \| u_t + c \|_{L^1(\Omega)}$.
    Since norms are convex, it follows that $u_t$ is the potential with minimal $L^1$ norm. 
\end{example}
